\documentclass{article}
\oddsidemargin  0.0in
\evensidemargin 0.0in
\textwidth      6.5in
\usepackage{tabularx}
\usepackage{html}
\title{\textbf{CASPER Library} \\Reference Manual}
\newcommand{\Block}[6]{\section {#1 \emph{(#2)}} \label{#3} \textbf{Block Author}: #4 \\ \textbf{Document Author}: #5 \subsection*{Summary}#6}

\newenvironment{PortTable}{\subsection*{Ports}
\tabularx{6.5in}{|l|l|l|X|} \hline  \textbf{Port} & \textbf{Dir.} & \textbf{Data Type} & \textbf{Description} \\ \hline}{\endtabularx}

\newcommand{\Port}[4]{\emph{#1} & \lowercase{#2} & #3 & #4\\  \hline}

\newcommand{\BlockDesc}[1]{\subsection*{Description}#1}

\newenvironment{ParameterTable}{\subsection*{Mask Parameters}
\tabularx{6.5in}{|l|l|X|} \hline  \textbf{Parameter} & \textbf{Variable} & \textbf{Description} \\ \hline}{\endtabularx}

\newcommand{\Parameter}[3]{#1 & \emph{#2} & #3 \\ \hline}

\begin{htmlonly}
\newcommand{\tabularx}[3]{\begin{tabularx}{#1}{#2}{#3}}
\newcommand{\endtabularx}{\end{tabularx}}
\end{htmlonly}

\date{Last Updated \today}
\begin{document}
\maketitle

%\chapter{System Blocks}
%%%%Change Chapter%%%%%%%%
%\chapter{Signal Processing Blocks}

%\input{test.tex}
%\chapter{Communication Blocks}
%\end{document} 

\Block{Decimating FIR Filter}{dec\_fir}{decfir}{Aaron Parsons}{Aaron Parsons, Ben Blackman}{FIR filter which can handle multiple time samples in parallel and decimates down to 1 time sample. If coefficiencts are symmetric, it will automatically fold before multiplying.}

\begin{ParameterTable}
\Parameter{Number of Parallel Streams}{n\_inputs}{The number of time samples which arrive in parallel.}
\Parameter{Coefficients}{coeff}{The FIR coefficients. If this vector is symmetric, the FIR will automatically fold before multiplying.}
\Parameter{Bit Width Out}{n\_bits}{The number of bits in each real/imag sample of the complex number that is output.}
\Parameter{Quantization Behavior}{quantization}{The quantization behavior used in converting to the output bit width.}
\Parameter{Add Latency}{add\_latency}{The latency of adders/converters.}
\Parameter{Mult Latency}{mult\_latency}{The latency of multipliers.}
\end{ParameterTable}

\begin{PortTable}
\Port{sync\_in}{IN}{boolean}{Takes an impulse 1 cycle before input is valid.}
\Port{realX}{IN}{Fix\_(n\_bits)\_(n\_bits-1)}{Real input X}
\Port{inagX}{IN}{Fix\_(n\_bits)\_(n\_bits-1)}{Imaginary input X}
\Port{sync\_out}{OUT}{boolean}{Will be high the clock cycle before \textit{dout} is valid.}
\end{PortTable}

\BlockDesc{
\paragraph{Usage}
User specifies the number of parallel streams to be decimated to one complex number. Inputs are multiplied by the coefficients and added together to form \textit{dout}. Bit Width Out specifies the widths of the real and imaginary components of the complex number to be output (Ex. if Bit Width Out = 8, then dout will be 16 bits, 8 for the real and imaginary components).
 }
 
\end{document}
