\documentclass{article}
\oddsidemargin  0.0in
\evensidemargin 0.0in
\textwidth      6.5in
\usepackage{tabularx}
\usepackage{html}
\title{\textbf{CASPER Library} \\Reference Manual}
\newcommand{\Block}[6]{\section {#1 \emph{(#2)}} \label{#3} \textbf{Block Author}: #4 \\ \textbf{Document Author}: #5 \subsection*{Summary}#6}

\newenvironment{PortTable}{\subsection*{Ports}
\tabularx{6.5in}{|l|l|l|X|} \hline  \textbf{Port} & \textbf{Dir.} & \textbf{Data Type} & \textbf{Description} \\ \hline}{\endtabularx}

\newcommand{\Port}[4]{\emph{#1} & \lowercase{#2} & #3 & #4\\  \hline}

\newcommand{\BlockDesc}[1]{\subsection*{Description}#1}

\newenvironment{ParameterTable}{\subsection*{Mask Parameters}
\tabularx{6.5in}{|l|l|X|} \hline  \textbf{Parameter} & \textbf{Variable} & \textbf{Description} \\ \hline}{\endtabularx}

\newcommand{\Parameter}[3]{#1 & \emph{#2} & #3 \\ \hline}

\begin{htmlonly}
\newcommand{\tabularx}[3]{\begin{tabularx}{#1}{#2}{#3}}
\newcommand{\endtabularx}{\end{tabularx}}
\end{htmlonly}

\date{Last Updated \today}
\begin{document}
\maketitle

%\chapter{System Blocks}
%%%%Change Chapter%%%%%%%%
%\chapter{Signal Processing Blocks}

%\input{test.tex}
%\chapter{Communication Blocks}
%\end{document} 



\Block{FIR Tap}{fir\_tap}{firtap}{Aaron Parsons}{Ben Blackman}{This block multiplies both inputs by \textit{factor} and outputs the result immediately after the multiply and outputs a delayed copy of the input by 1 cycle,}


\begin{ParameterTable}
\Parameter{Factor}{factor}{The value that multiplies both inputs.}
\Parameter{Mult latency}{latency}{The latency of the multiplier.}
\end{ParameterTable}

\begin{PortTable}
\Port{a}{IN}{Inherited}{The first number to be multiplied by \textit{factor}. It usually is the real component of an input.}
\Port{b}{IN}{Inherited}{The second number to be multiplied by \textit{factor}. It usually is the imaginary component of an input.}
\Port{a\_out}{OUT}{Inherited}{The input \textit{a} delayed by 1 cycle.}
\Port{b\_out}{OUT}{Inherited}{The input \textit{b} delayed by 1 cycle.}
\Port{real}{OUT}{Inherited}{The result of the multiplication of \textit{a} with \textit{factor}.}
\Port{imag}{OUT}{Inherited}{The result of the multiplication of \textit{b} with \textit{factor}.}
\end{PortTable}

\BlockDesc{
\paragraph{Usage}
\textit{a\_out} and \textit{b\_out} are 1 cycle delayed versions of \textit{a} and \textit{b}, respectively. \textit{real} and \textit{imag} are the results of \textit{a} * \textit{factor} and \textit{b} * \textit{factor}, respectively. The delay from \textit{a} to \textit{real} or \textit{b} to \textit{imag} is equal to \textit{latency}. 
 }
 
\end{document}
