\documentclass{article}
\oddsidemargin  0.0in
\evensidemargin 0.0in
\textwidth      6.5in
\usepackage{tabularx}
\usepackage{html}
\title{\textbf{CASPER Library} \\Reference Manual}
\newcommand{\Block}[6]{\section {#1 \emph{(#2)}} \label{#3} \textbf{Block Author}: #4 \\ \textbf{Document Author}: #5 \subsection*{Summary}#6}

\newenvironment{PortTable}{\subsection*{Ports}
\tabularx{6.5in}{|l|l|l|X|} \hline  \textbf{Port} & \textbf{Dir.} & \textbf{Data Type} & \textbf{Description} \\ \hline}{\endtabularx}

\newcommand{\Port}[4]{\emph{#1} & \lowercase{#2} & #3 & #4\\  \hline}

\newcommand{\BlockDesc}[1]{\subsection*{Description}#1}

\newenvironment{ParameterTable}{\subsection*{Mask Parameters}
\tabularx{6.5in}{|l|l|X|} \hline  \textbf{Parameter} & \textbf{Variable} & \textbf{Description} \\ \hline}{\endtabularx}

\newcommand{\Parameter}[3]{#1 & \emph{#2} & #3 \\ \hline}

\begin{htmlonly}
\newcommand{\tabularx}[3]{\begin{tabularx}{#1}{#2}{#3}}
\newcommand{\endtabularx}{\end{tabularx}}
\end{htmlonly}

\date{Last Updated \today}
\begin{document}
\maketitle

%\chapter{System Blocks}
%%%%Change Chapter%%%%%%%%
%\chapter{Signal Processing Blocks}

%\input{test.tex}
%\chapter{Communication Blocks}
%\end{document} 

\Block{Stopwatch}{stopwatch}{stopwatch}
{Jason Manley}
{Jason Manley}
{Counts the number of clocks between a start and stop pulse.}


\begin{ParameterTable}
\Parameter{None}{None}{This block has no parameters}
\end{ParameterTable}

\begin{PortTable}
\Port{start}{in}{boolean}{Start counting}
\Port{stop}{in}{boolean}{Stop counting and hold value until reset received}
\Port{reset}{in}{boolean}{Reset back to zero.}
\Port{count\_out}{out}{ufix\_32\_0}{Number of clocks elapsed since start pulse received.}
\end{PortTable}

\BlockDesc{This block counts the number of clocks between a start and stop pulse. This value is held until a reset is received. If another start pulse is received before the reset, counting resumes from where it left-off. If a reset is received mid-way through a count (ie before a stop pulse) then the stopwatch will be reset and await another start pulse before it restarts counting. Test Model: test\_stopwatch.mdl}


 
\end{document}
