\documentclass{article}
\oddsidemargin  0.0in
\evensidemargin 0.0in
\textwidth      6.5in
\usepackage{tabularx}
\usepackage{html}
\title{\textbf{CASPER Library} \\Reference Manual}
\newcommand{\Block}[6]{\section {#1 \emph{(#2)}} \label{#3} \textbf{Block Author}: #4 \\ \textbf{Document Author}: #5 \subsection*{Summary}#6}

\newenvironment{PortTable}{\subsection*{Ports}
\tabularx{6.5in}{|l|l|l|X|} \hline  \textbf{Port} & \textbf{Dir.} & \textbf{Data Type} & \textbf{Description} \\ \hline}{\endtabularx}

\newcommand{\Port}[4]{\emph{#1} & \lowercase{#2} & #3 & #4\\  \hline}

\newcommand{\BlockDesc}[1]{\subsection*{Description}#1}

\newenvironment{ParameterTable}{\subsection*{Mask Parameters}
\tabularx{6.5in}{|l|l|X|} \hline  \textbf{Parameter} & \textbf{Variable} & \textbf{Description} \\ \hline}{\endtabularx}

\newcommand{\Parameter}[3]{#1 & \emph{#2} & #3 \\ \hline}

\begin{htmlonly}
\newcommand{\tabularx}[3]{\begin{tabularx}{#1}{#2}{#3}}
\newcommand{\endtabularx}{\end{tabularx}}
\end{htmlonly}

\date{Last Updated \today}
\begin{document}
\maketitle

%\chapter{System Blocks}
%%%%Change Chapter%%%%%%%%
%\chapter{Signal Processing Blocks}

%\input{test.tex}
%\chapter{Communication Blocks}
%\end{document} 
\Block{The Programmable Sync Delay Block}{sync\_delay\_prog}{syncdelayprog}{Aaron Parsons}{Aaron Parsons}{Delay an infrequent boolean pulse by a run-time programmable number of enabled clocks. If the input pulse repeats before the output pulse is generated, an internal counter resets and that output pulse is never generated. When delay is changed, some randomly determined samples will be inserted/dropped from the buffered stream.}



\begin{ParameterTable}

\Parameter{Max Delay (2$^?$):}{MaxDelay}{The maximum length of the delay.}

\end{ParameterTable}



\begin{PortTable}

\Port{sync}{in}{???}{The boolean signal to be delayed.}

\Port{delay}{in}{???}{The run-time programmable delay length.}

\Port{sync\_out}{out}{???}{The delayed boolean signal.}

\end{PortTable}



\BlockDesc{Delay an infrequent boolean pulse by a run-time programmable number of enabled clocks. If the input pulse repeats before the output pulse is generated, an internal counter resets and that output pulse is never generated. When delay is changed, some randomly determined samples will be inserted/dropped from the buffered stream.} 
\end{document}
