\documentclass{article}
\oddsidemargin  0.0in
\evensidemargin 0.0in
\textwidth      6.5in
\usepackage{tabularx}
\usepackage{html}
\title{\textbf{CASPER Library} \\Reference Manual}
\newcommand{\Block}[6]{\section {#1 \emph{(#2)}} \label{#3} \textbf{Block Author}: #4 \\ \textbf{Document Author}: #5 \subsection*{Summary}#6}

\newenvironment{PortTable}{\subsection*{Ports}
\tabularx{6.5in}{|l|l|l|X|} \hline  \textbf{Port} & \textbf{Dir.} & \textbf{Data Type} & \textbf{Description} \\ \hline}{\endtabularx}

\newcommand{\Port}[4]{\emph{#1} & \lowercase{#2} & #3 & #4\\  \hline}

\newcommand{\BlockDesc}[1]{\subsection*{Description}#1}

\newenvironment{ParameterTable}{\subsection*{Mask Parameters}
\tabularx{6.5in}{|l|l|X|} \hline  \textbf{Parameter} & \textbf{Variable} & \textbf{Description} \\ \hline}{\endtabularx}

\newcommand{\Parameter}[3]{#1 & \emph{#2} & #3 \\ \hline}

\begin{htmlonly}
\newcommand{\tabularx}[3]{\begin{tabularx}{#1}{#2}{#3}}
\newcommand{\endtabularx}{\end{tabularx}}
\end{htmlonly}

\date{Last Updated \today}
\begin{document}
\maketitle

%\chapter{System Blocks}
%%%%Change Chapter%%%%%%%%
%\chapter{Signal Processing Blocks}

%\input{test.tex}
%\chapter{Communication Blocks}
%\end{document} 
\Block{X-Engine TVG}{xeng\_tvg}{xengtvg}
{Jason Manley}
{Jason Manley}
{Basic test vector generator for CASPER X-engines.}

\begin{ParameterTable}
\Parameter{Number of Antennas ($2^n$)}{ant\_bits}{Bitwidth of the number of antennas in the system.}
\Parameter{Bitwidth of Samples in}{bits\_in}{Bitwidth of component of the input.}
\Parameter{X integration length ($2^n$)}{x\_int\_bits}{Bitwidth of X-engine accumulation length.}
\Parameter{Sync Pulse Period ($2^n$)}{sync\_period}{Bitwidth of number of valids between sync pulses.}
\end{ParameterTable}

\begin{PortTable}
\Port{tvg\_sel}{in}{ufix\_2\_0}{TVG selection. 0=off (passthrough), 1-3=TVG select.}
\Port{data\_in}{in}{inherited: bits\_in*4}{Data in for passthrough.}
\Port{valid\_in}{in}{boolean}{Valid in made available for passthrough.}
\Port{sync\_in}{in}{boolean}{Sync in made available for passthrough.}
\Port{data\_out}{out}{inherited: bits\_in*4}{Port Description}
\Port{sync\_out}{out}{boolean}{Port Description}
\Port{valid\_out}{out}{boolean}{Port Description}
\end{PortTable}

\BlockDesc{
This block generates data in a format suitable for input to a CASPER X-engine. The \textit{tvg\_sel} line selects the TVG. If set to zero, it is configured for passthrough and all input signals are propagated to the output (TVG is off). Values one through three select a TVG pattern. In this case, sync pulses are generated internally and valid data is output all the time. The three patterns are as follows:

\begin{enumerate}
\item Inserts a counter representing the antenna number. All real values count up from zero and imaginary values counting down from zero. ie antenna four would have the value \textit{4 - 4i} inserted.
\item Inserts the same constant for all antennas: $Pol_{1real}=0.125$, $Pol_{1imag}=-0.75$, $Pol_{2real}=0.5$ and $Pol_{2imag}=-0.25$
\item User selectable values for each antenna. Input registers named \textit{tv0} through \textit{tv7} are input cyclically. Each value is input for \textit{x\_int\_bits} clocks.
\end{enumerate}

} 
\end{document}
