\documentclass{article}
\oddsidemargin  0.0in
\evensidemargin 0.0in
\textwidth      6.5in
\usepackage{tabularx}
\usepackage{html}
\title{\textbf{CASPER Library} \\Reference Manual}
\newcommand{\Block}[6]{\section {#1 \emph{(#2)}} \label{#3} \textbf{Block Author}: #4 \\ \textbf{Document Author}: #5 \subsection*{Summary}#6}

\newenvironment{PortTable}{\subsection*{Ports}
\tabularx{6.5in}{|l|l|l|X|} \hline  \textbf{Port} & \textbf{Dir.} & \textbf{Data Type} & \textbf{Description} \\ \hline}{\endtabularx}

\newcommand{\Port}[4]{\emph{#1} & \lowercase{#2} & #3 & #4\\  \hline}

\newcommand{\BlockDesc}[1]{\subsection*{Description}#1}

\newenvironment{ParameterTable}{\subsection*{Mask Parameters}
\tabularx{6.5in}{|l|l|X|} \hline  \textbf{Parameter} & \textbf{Variable} & \textbf{Description} \\ \hline}{\endtabularx}

\newcommand{\Parameter}[3]{#1 & \emph{#2} & #3 \\ \hline}

\begin{htmlonly}
\newcommand{\tabularx}[3]{\begin{tabularx}{#1}{#2}{#3}}
\newcommand{\endtabularx}{\end{tabularx}}
\end{htmlonly}

\date{Last Updated \today}
\begin{document}
\maketitle

%\chapter{System Blocks}
%%%%Change Chapter%%%%%%%%
%\chapter{Signal Processing Blocks}

%\input{test.tex}
%\chapter{Communication Blocks}
%\end{document} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%Snap64 Block%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\Block{64 Bit Snapshot}{snap64}{snap64}{Aaron Parsons}{Aaron Parsons, Ben Blackman}{The snap block provides a packaged solution to capturing data from the FPGA fabric and making it accessible from the CPU. snap64 captures to 2x32 bit wide shared BRAMs to effect a 64 bit capture.}

\begin{ParameterTable}
\Parameter{No. of Samples ($2^?$)}{nsamples}{Specifies the depth of the Shared BRAM(s); i.e. the number of 64bit samples which are stored per capture.}
\end{ParameterTable}

\begin{PortTable}
\Port{din}{IN}{unsigned\_64\_0}{The data to be captured. Regardless of type, the bit-level representation of these numbers are written as 64bit values to the Shared BRAMs.}
\Port{trig}{IN}{boolean}{When high, triggers the beginning of a data capture. Thereafter, every enabled data is written to the shared BRAM until it is full.}
\Port{we}{IN}{boolean}{After a trigger is begun, enables a write to Shared BRAM.}
\end{PortTable}

\BlockDesc{
\paragraph{Usage}
Under TinySH/BORPH, this device will have 3 sub-devices: \textit{ctrl}, \textit{bram\_msb}, \textit{bram\_lsb}, and \textit{addr}. \textit{ctrl} is an input register. Bit 0, when driven from low to high, enables a trigger/data capture to occur. Bit 1, when high, overrides \textit{trig} to trigger instantly. Bit 2, when high, overrides \textit{we} to always write data to bram. \textit{addr} is an output register and records the last address of bram to which data was written. \textit{bram\_msb} and \textit{bram\_lsb} are 32 bit wide Shared BRAMs of the depth specified in \textit{Parameters}. \textit{bram\_msb} holds the upper 32 bits of \textit{din} while \textit{bram\_lsb} holds the lower 32 bits of \textit{din}.
}
 
\end{document}
