\documentclass{article}
\oddsidemargin  0.0in
\evensidemargin 0.0in
\textwidth      6.5in
\usepackage{tabularx}
\usepackage{html}
\title{\textbf{CASPER Library} \\Reference Manual}
\newcommand{\Block}[6]{\section {#1 \emph{(#2)}} \label{#3} \textbf{Block Author}: #4 \\ \textbf{Document Author}: #5 \subsection*{Summary}#6}

\newenvironment{PortTable}{\subsection*{Ports}
\tabularx{6.5in}{|l|l|l|X|} \hline  \textbf{Port} & \textbf{Dir.} & \textbf{Data Type} & \textbf{Description} \\ \hline}{\endtabularx}

\newcommand{\Port}[4]{\emph{#1} & \lowercase{#2} & #3 & #4\\  \hline}

\newcommand{\BlockDesc}[1]{\subsection*{Description}#1}

\newenvironment{ParameterTable}{\subsection*{Mask Parameters}
\tabularx{6.5in}{|l|l|X|} \hline  \textbf{Parameter} & \textbf{Variable} & \textbf{Description} \\ \hline}{\endtabularx}

\newcommand{\Parameter}[3]{#1 & \emph{#2} & #3 \\ \hline}

\begin{htmlonly}
\newcommand{\tabularx}[3]{\begin{tabularx}{#1}{#2}{#3}}
\newcommand{\endtabularx}{\end{tabularx}}
\end{htmlonly}

\date{Last Updated \today}
\begin{document}
\maketitle

%\chapter{System Blocks}
%%%%Change Chapter%%%%%%%%
%\chapter{Signal Processing Blocks}

%\input{test.tex}
%\chapter{Communication Blocks}
%\end{document} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%SRAM Block
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\Block{SRAM}{sram}{sram}{Pierre Yves Droz, Henry Chen}{Ben Blackman}{The sram block represents a 36x512k SRAM chip on the IBOB. It stores 36-bit words and requires 19 bits to access its address space.}


\begin{ParameterTable}
\Parameter{SRAM}{sram}{Selects which SRAM chip this block represents.}
\Parameter{Data Type}{arith\_type}{Type to which the data is cast on both the input and output.}
\Parameter{Data binary point (bitwidth is 36)}{bin\_pt}{Position of the binary point of the data.}
\Parameter{Sample period}{sample\_period}{Sets the period with reference to the clock frequency.}
\Parameter{Simulate SRAM using ModelSim}{use\_sim}{Turns ModelSim simulation on or off.}
\end{ParameterTable}

\begin{PortTable}
\Port{we}{IN}{boolean}{A signal that when high, causes the data on data\_in to be written to address.}
\Port{be}{IN}{unsigned\_4\_0}{A signal that enables different 9-bit bytes of data\_in to be written.}
\Port{address}{IN}{unsigned\_19\_0}{A signal that specifies the address where either data\_in is to be stored or from where data\_out is to be read.}
\Port{data\_in}{IN}{arith\_type\_36}{A signal that contains the data to be stored.}
\Port{data\_out}{OUT}{arith\_type\_36}{A signal that contains the data coming out of address.}
\Port{data\_valid}{OUT}{boolean}{A signal that is high when data\_out is valid.}
\end{PortTable}

\BlockDesc{
\paragraph{Usage}
The SRAM block is 36x512k, signifying that its input and output are 36-bit words and it can store 512k words. Each clock cyle, if \textit{we} is high, then each bit of be determines whether each 9-bit chunk will be written to address. \textit{be} is 4 bits with the highest bit corresponding to the most significant chunk (so if \textit{be} is 1100, only the top 18 bits will be written). If \textit{we} is low, then the SRAM block ignores \textit{data\_in} and be and reads the word stored at \textit{address}.
}
 
\end{document}
