\documentclass{article}
\oddsidemargin  0.0in
\evensidemargin 0.0in
\textwidth      6.5in
\usepackage{tabularx}
\usepackage{html}
\title{\textbf{CASPER Library} \\Reference Manual}
\newcommand{\Block}[6]{\section {#1 \emph{(#2)}} \label{#3} \textbf{Block Author}: #4 \\ \textbf{Document Author}: #5 \subsection*{Summary}#6}

\newenvironment{PortTable}{\subsection*{Ports}
\tabularx{6.5in}{|l|l|l|X|} \hline  \textbf{Port} & \textbf{Dir.} & \textbf{Data Type} & \textbf{Description} \\ \hline}{\endtabularx}

\newcommand{\Port}[4]{\emph{#1} & \lowercase{#2} & #3 & #4\\  \hline}

\newcommand{\BlockDesc}[1]{\subsection*{Description}#1}

\newenvironment{ParameterTable}{\subsection*{Mask Parameters}
\tabularx{6.5in}{|l|l|X|} \hline  \textbf{Parameter} & \textbf{Variable} & \textbf{Description} \\ \hline}{\endtabularx}

\newcommand{\Parameter}[3]{#1 & \emph{#2} & #3 \\ \hline}

\begin{htmlonly}
\newcommand{\tabularx}[3]{\begin{tabularx}{#1}{#2}{#3}}
\newcommand{\endtabularx}{\end{tabularx}}
\end{htmlonly}

\date{Last Updated \today}
\begin{document}
\maketitle

%\chapter{System Blocks}
%%%%Change Chapter%%%%%%%%
%\chapter{Signal Processing Blocks}

%\input{test.tex}
%\chapter{Communication Blocks}
%\end{document} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%Template for documenting CASPER Library Blocks%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Block{DAC}{dac}{dac}{Henry Chen}{Ben Blackman}{The DAC block converts 4 digital inputs to 1 analog output. The \textit{dac} runs at 4x FPGA clock frequency, outputting analog converted samples 0 through 3 each FPGA clock cycle.}


\begin{ParameterTable}
\Parameter{DAC board}{dac\_brd}{Select which IBOB port to run this \textit{dac}.}
\Parameter{DAC clock rate (MHz)}{dac\_clk\_rate}{The clock rate to run the \textit{dac}. Must be 4x FPGA clock rate.}
\Parameter{Sample period}{sample\_period}{Sets the period at which the \textit{dac} outputs samples (ie 2 means every other cycle).}
\Parameter{Show Implementation Parameters}{show\_param}{Allows the user to set the implementation parameters.}
\Parameter{Invert output clock phase}{invert\_clock}{When unchecked, the \textit{dac} samples the data aligned with the clock. When checked, the \textit{dac} samples the data aligned with an inverted clock.}
\end{ParameterTable}

\begin{PortTable}
\Port{dataX}{IN}{Fix\_9\_8}{One of 4 digital inputs to be converted to analog.}
\Port{sim\_out}{OUT}{double}{Analog output of \textit{dac}. Note: For simulation only.}
\end{PortTable}

\BlockDesc{
\paragraph{Usage}
The \textit{dac} takes 4 \textit{Fix\_9\_8} inputs and outputs an analog stream. The \textit{dac} runs at 4x the FPGA clock speed.
\\
\\
To be updated.
}
 
\end{document}
